Introductory Physics Labs: A Tale of Two Transformations

### 2021-05-05 manuscript/onlineLabPaper.tex
Missed a citation when I unmasked.  Have fixed this and re-made the word doc.

The transition to online learning has not gone without hiccups.  Technology and access are two
key factors for success in online learning environments, which were a barrier for many of our
students.  Our institution implemented a number of academic measures intended to support our
students during the pandemic, including extending the withdrawal date and allowing students to
be graded pass/fail after seeing their final grade during each of the Spring 2020 and Fall 2020
semesters. Other supports put in place at the institution included an extended laptop loan
program. Also, remote proctoring was paid for by a grant through the university system. Our
institution's Center for Survey Research published some findings in August 2020 that explain
some of our observed issues.\citep{ECUcovidSurveyRedacted} The GTAs and students found
communication about proposals much more difficult online than in face-to-face classes.  About
\SI{10}{\percent} to \SI{20}{\percent} of our students did not have reliable internet access
after the transition to online learning in the spring.\citep{ECUcovidSurveyRedacted} Also, up
to \SI{8}{\percent} of students did not have access to a computer once they left
campus.\citep{ECUcovidSurveyRedacted} Additionally, we noticed that some students in the course
did not have access to computers capable of running \emph{Tracker} or \emph{ImageJ}, both of
which run on Windows, Macintosh, or Linux computers but not Chromebooks or mobile devices. We
discovered \emph{jsTrack}\citep{jstrack}, an online Javascript web application for video
analysis that runs on most computers including Chromebooks, but not mobile devices.

>>>>

The transition to online learning has not gone without hiccups.  Technology and access are two
key factors for success in online learning environments, which were a barrier for many of our
students.  Our institution implemented a number of academic measures intended to support our
students during the pandemic, including extending the withdrawal date and allowing students to
be graded pass/fail after seeing their final grade during each of the Spring 2020 and Fall 2020
semesters. Other supports put in place at the institution included an extended laptop loan
program. Also, remote proctoring was paid for by a grant through the university system. Our
institution's Center for Survey Research published some findings in August 2020 that explain
some of our observed issues.\citep{ECUcovidSurvey} The GTAs and students found
communication about proposals much more difficult online than in face-to-face classes.  About
\SI{10}{\percent} to \SI{20}{\percent} of our students did not have reliable internet access
after the transition to online learning in the spring.\citep{ECUcovidSurvey} Also, up
to \SI{8}{\percent} of students did not have access to a computer once they left
campus.\citep{ECUcovidSurvey} Additionally, we noticed that some students in the course
did not have access to computers capable of running \emph{Tracker} or \emph{ImageJ}, both of
which run on Windows, Macintosh, or Linux computers but not Chromebooks or mobile devices. We
discovered \emph{jsTrack}\citep{jstrack}, an online Javascript web application for video
analysis that runs on most computers including Chromebooks, but not mobile devices.
